---
title: "TASK-2"
author: "Ankur Kumar Singh"
date: "06/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# LOADING AND PREPROCESSING THE DATASET

```{r}
setwd("D:/rrrrr")
data <- read.csv("iris.csv")
data_species <- data[,"Species"] # Taking Species
data_value <- data[,c(2,3,4,5)] # Taking Values
head(data_value,5)

```
# GENERAL DESCRIPTION OF DATA

```{r}
summary(data)
```

# LOADING PACKAGES

```{r}
library(factoextra) # Visualizing the clusters
library(NbClust) # Running estimation for optimal number of clusters
library(heatmaply) # Used for normalizing the data

```
# NORMALIZING THE DATA

```{r}

data_value <- normalize(data_value) # Running min-max scaling 
```

# ESTIMATING OPTIMAL NUMBER OF CLUSTERS

```{r}

fviz_nbclust(data_value, kmeans, nstart = 25,  method = "gap_stat", nboot = 50)+
  labs(subtitle = "Gap statistic method")
# GAP STATISTIC IS PREFFERED BECAUSE IT PROVIDES WELL DEFINED STATISTICAL PROCEDURE TO ESTIMATE THE OPTIMAL NUMBER OF CLUSTERS
```

# RUNNING KMEANS ALGORITHM

```{r}
set.seed(123)
km.res <- kmeans(data_value,3,nstart = 10)
```

# MODEL RESULTS
```{r}
km.res
```


# VISUALIZING THE CLUSTERS
```{r}
fviz_cluster(km.res, data_value, ellipse.type = "norm", geom = "text") 

```

# GENERATING TABLE

```{r}
table(km.res$cluster,data_species)
```

# TABLE RESULTS

```{r}
# FROM TABLE
# ROW 1 <- SETOSA
# ROW 2 <- VIRGINICA
# ROW 3 <- VERISCOLOR
c_classified = sum(50,47,36)
i_classified = sum(3,14)
accuracy = 133/sum(c_classified,i_classified)
values <- data.frame("Classified COrrectly"=c_classified,"Classified Incorrectly"=i_classified ,"Accuracy(%)"=accuracy)
values


```

# CONCLUSION

1. Clusters with size 50,39 and 61 are created successfully
2. From Gap-statistic method optimum number of cluster was found
3. WSS(Within Sum of Square) accuracy is 83%
4. 133 instances are calssified correctly while 17 of them are classified incorrectly with an accuracy 88.6%